---
title: "Midterm: Examing Gender Pay Gap with Bayesian Regression"
author: "Emma Kruis"
date: "2020-02-01"
output:
  pdf_document: default
  word_document: default
  html_notebook: default
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---

## Instructions

This script reviews *Bayesian Regression Analysis* as part of the *Midterm Review*. 
You will use content from the lecture and assignment materials on *Bayesian Regression Analysis* to complete this script.
You will *copy and paste* relevant code from those files into this script and answer the associated questions for each task. 
You will respond to questions in each section after executing relevant code to answer a question. 
You will submit this script to its *Submissions* folder on *D2L* as part of the *Midterm Review*.
For this script, you will submit *two* files:

1. this completed *R Markdown* script, and 
2. as a first preference, a *PDF* (if you already installed `TinyTeX` properly), as a second preference, a *Microsfot Word* (if your computer has *Microsoft Word*) document, or, as a third preference, an *HTML* (if you did *not* install `TinyTeX` properly and your computer does *not* have *Microsoft Word*) file to *D2L*.

For the *Midterm Review*, create the project directory: *~/mgt_592/assignments/midterm_review*.
Convert your project directory into a formal *R Project* directory by going to the *File* menu in *RStudio*, selecting *New Project...*, choosing *Existing Directory*, and going to your *~/mgt_592/assignments/midterm_review* folder to select it as the top-level directory for this **R Project**.  
The project directory should contain the following folders: *scripts*, *data*, and *plots*.
Store this script in the *scripts* folder and the relevant data in the *data* folder.

## Global Settings

The first code chunk sets the global settings for the remaining code chunks in the document.
Do *not* change anything in this code chunk.

```{r, setup, include = FALSE}
### specify echo setting for all code chunks
## call function
knitr::opts_chunk$set(echo = TRUE)
```

## Task 1: Load Libraries

For this task, you will load the libraries you need for this script.

### Task 1.1

In this code chunk, load the following packages:

1. **here**,
2. **tidyverse**,
3. **janitor**,
4. **skimr**, 
5. **ggthemes**,
6. **rstanarm**,
7. **bayesplot**, and
8. **tidybayes**.

Make sure you installed these packages before loading the libraries.

You will use functions from these packages to complete this script. 

```{r, task1_1}
### load libraries for use in current working session
## here for project work flow
library(here)

## tidyverse for data manipulation and plotting
## loads eight different libraries simultaneously
library(tidyverse)

## janitor to clean data and chi-square test
library(janitor)

## skimr to summarize data
library(skimr)

## ggthemes for plot themes
library(ggthemes)

## rstanarm for Bayesian regression
library(rstanarm)

## bayesplot for Bayesian posterior distributions
library(bayesplot)

## tidybayes to work with Bayesian model results
library(tidybayes)
```

## Task 2: Import Data

For this task, you will import the data file: **gender_pay_gap.csv**.

### Task 2.1

Use the **read_csv()** and **here()** functions to load the data file for this working session. 
Save the data as the object **org_raw**. 

Make a copy of the data and name the copy: **org_work**.
You will work with the *complete data*.
Use the **glimpse()** function to view a preview of values for each variable in **org_work**. 

```{r, task2_1}
org_raw<- read_csv(
  here("data", "gender_pay_gap.csv")
)

org_work <- org_raw 


glimpse(org_work)
```

## Task 3: Clean and Prepare Data

For this task, you will clean and prepare the data.

### Task 3.1

Perform the following cleaning tasks to update **org_work**: 

1. mutate all character variables to factor variables, and
2. use **clean_names()** to make variable names use all lowercase letters and connect multiple words with underscores.

Use **glimpse()** to preview the updated **org_work** data object.

```{r, task3_1}
org_work <- org_work %>%
  mutate(
    across(
      .cols = where(is.character),
      .fns = as_factor
    )
  ) %>%
  clean_names()

glimpse(org_work)
```

## Task 4: Examine Data

For this task, you will examine the data.

### Task 4.1

Create a plot using **ggplot()** to highlight the differences in *base pay* between *men* and *women* for different *departments*.

Do the following:

1. call **ggplot()**, set the data to **org_work**, map **gender** to the *x-axis* and the **fill**, and map **base_pay** to the *y-axis*;
2. call **geom_boxplot()** and set the outlier **color** to **purple** and **size** to **1.5**;
3. call **geom_point()** and set **alpha** to **0.15**;
4. call **facet_wrap()** to facet by **dept** with **2** rows;
5. call **scale_y_continuous** and set the number of breaks to **8** and the **labels** to *dollar format*;
6. label the axes and legend appropriately with **labs()**;
7. use **theme_fivethirtyeight()** as the *theme*.

**Questions 4.1**: Answer these questions:
(1) For which combinations of *department* and *gender* are there outliers?
(2) Is the *median total pay* higher for *women* in any of the *department* groups?

**Responses 4.1**: *(1) management and sales (2) No *.

```{r, task4_1}
ggplot(
  org_work,
  aes(x =gender, y = base_pay, fill = gender)
) +
  geom_boxplot(outlier.color = "purple", outlier.size = 1.5) +
  geom_point(alpha = 0.15) +
  facet_wrap(
    vars(dept),
    nrow = 2,
    labeller = as_labeller(
      setNames(
      paste("Department", levels(org_work$dept), sep = ": "),
      levels(org_work$dept)
      )
    )
  )+
  scale_y_continuous(n.breaks = 8, labels = scales::dollar_format()) + 
  labs(x = "Gender", Y = "Base Pay", fill= "Gender") +
  theme_fivethirtyeight()
```

## Task 5: Fit Moderated Bayesian Regression Model

Estimate a simple Bayesian regression model using using **org_work** where observed values of *base pay* are predicted from observed values of *gender* and *department*.

### Task 5.1

Create a model object named **mod_1** using **stan_glm()**.
Inside of **stan_glm()**, do the following:

1. specify the *formula* to indicate **base_pay** predicted by **gender**, **dept**, and their interaction,
2. specify the *data* as **org_work**,
3. set the *prior intercept* to a **normal** distribution with **location** equal to **8e4** and **autoscale** equal to **TRUE**,
4. set the *prior of the regression coefficients for the predictors* to a **normal** distribution with **location** equal to **0** and **autoscale** equal to **TRUE**,
5. set the *error prior* to be an **exponential** distribution with **rate** equal to **0.7** and **autoscale** equal to **TRUE**, and
6. set the **seed** to **1805** (birth year of *William Rowan Hamilton*).

After creating the model, then do the following:

1. apply **summary()** to **mod_1** using *three digits* and **seq(0.1, 0.9, 0.2)** for the *percentiles* to examine the posterior parameter distributions,
2. apply **coef()** to **mod_1** to extract the *median* regression coefficients, and
3. apply **posterior_interval** to **mod_1** and set the *credible interval* to **0.89**.

**Questions 5.1**: Answer these questions:
(1) What is the *90th percentile* of the **genderMale:deptAdministration** regression coefficient?
(2) What is the estimated *median difference in base pay* between *men* and *women* in the *operations* department (i.e., look at the **genderMale** regression coefficient)?
(3) What is the *89% credible interval* for the difference in pay for *women* in the *management department* versus the *operations department* (i.e., look at the **deptManagement** row)?
(4) What is the *89% credible interval* for the difference in pay for *men* versus *women* in the *management department* (i.e., look at the **genderMale:deptManagement** row)?

**Responses 5.1**: *(1) 10618.898 (2) 8537.523 (3) 91825.96 (4) 11116.88*.

```{r, task5_1}
##model creation
mod_1 <- stan_glm(
  base_pay ~ gender,
  data = org_work,
  prior_intercept = normal(location= 8e+04, autoscale = TRUE),
  prior = normal(location = 0, autoscale = TRUE),
  prior_aux = exponential(rate = 0.7, autoscale = TRUE),
  seed = 1805
)


##model summary
summary(mod_1, digits = 3, probs = seq(0.1, 0.9,0.2))


##extracting coefficients
coef(mod_1)

##examine credible intervals
posterior_interval(mod_1, prob = 0.89)


```

### Task 5.2

Examine **mod_1** by doing the following:

1. compute the *Bayesian R-squared* using **bayes_R2()** and saving the results to an object named **mod_1_r_sq**;
2. apply **summary()** to **mod_1_r_sq**;
3. apply **pp_check()** and examine the *density overlay*, the *mean* on its own, and the *mean* and *sd* together;
4. compute the *fitted values* using the *median posterior regression parameters* and save the calculation as a new variable named **mod_1_fitted** to **org_work**;
5. open the *spreadsheet view* of **org_work** to answer a question about **mod_1_fitted** values.

**Questions 5.2**: Answer these questions:
(1) What is the *median R-squared* value?
(2) Do the *posterior predictive checks* indicate any estimation issues?
(3) Use the *spreadsheet view* of **org_work** to answer: what is the *median posterior fitted value* for a *female* employee working in the *engineering* department?
(4) Use the *spreadsheet view* of **org_work** to answer: what is the *median posterior fitted value* for a *male* employee working in the *engineering* department?

**Responses 5.2**: *(1) 0.028287 (2) No estimation issues (3) 89916.70 (4) 98454.23*.

```{r, task5_2}
mod_1_r_sq <- bayes_R2(mod_1)

summary(mod_1_r_sq)

##posterior predictive checks
#density overlay
pp_check(mod_1, "dens_overlay")

#mean
pp_check(mod_1, plotfun = "stat", stat= "mean")


#mean and sd
pp_check(mod_1, plotfun = "stat_2d", stat = c("mean", "sd"))

##median posterior fitted values
org_work <- org_work %>%
  mutate(mod_1_fitted = fitted(mod_1))

mod_1_fitted <- as_tibble(mod_1)


mod_1_fitted
```

### Task 5.3

Extract the draws from the posterior regression parameter distributions from **mod_1** with **as_tibble()** and save them as **mod_1post**.
Create a plot using **mcmc_areas()**.
Do the following to create the plot:

1. call **mcmc_areas()** and set data to **mod_1_post**, select the **`genderMale:deptSales`** (note the back ticks) parameter, and set the interval to **0.89**;
3. call **ggtitle()** and set the *title* of the plot to **Posterior Distribution for Gender Difference in Base Pay in Sales Department**.

**Question 5.3**: What can you say about the *gender difference in base pay in the sales department*?

**Response 5.3**: *This confirms that there is a gender pay gap even at the 100th percentile. *.

```{r, task5_3}
mod_1_post <- as_tibble(mod_1)

mod_1_post

#posterior parmeter distributions
mcmc_areas(
  mod_1_post,
  pars = vars(genderMale),
  prob = 0.89
)+
  
  ggtitle("Posterior Distribution for Gender Difference in Base Pay in Sales Department")
```

### Task 5.4

Calculate the *fitted* and *predicted* values from the *posterior draws* of the regression parameters where you set **gender** equal to **levels(org_work$gender)** (i.e., **gender = levels(org_work$gender)**) and **dept** equal to **levels(org_work$dept)** (i.e., **dept = levels(org_work$gender)**) inside of **crossing()**.
Pass the **crossing()** result to **add_fitted_draws()** and **add_predicted_draws()** while including **mod_1** as an input as well for the *fitted* and *predicted* values saving the results as **mod_1_post_fit** and **mod_1_post_pred**, respectively.

Create a plot named **mod_1_plot** using **ggplot()**.
To create the plot, do the following:

1. inside of **ggplot()**, set data to **org_work**, **gender** to the *x-axis*, and **base_pay** to the *y-axis*;
2. add a first **geom_jitter()** layer with **height** and **width** set to **0.05** and **alpha** set to **0.5**.
3. add a second **geom_jitter()** layer with **height** and **width** set to **0.05**, set data to **mod_1_post_pred**, map **gender** to the *x-axis* and **.prediction** to the *y-axis*, set **color** to **lightgreen**, set **size** to **0.5**, and set **alpha** to **0.15**;
4. add a third **geom_jitter()** layer with **height** and **width** set to **0.05**, set data to **mod_1_post_fit**, map **gender** to the *x-axis* and **.value** to the *y-axis*, set **color** to **skyblue**, set **size** to **1.5**, and set **alpha** to **0.15**;
5. add a **geom_point()** layer and map **mod_1_fitted** to the *y-axis*, set **color** to **red**, and set **size** to **2**;
6. add **facet_wrap()** to facet by **dept** across **2** rows;
7. call **scale_y_continuous** and set the number of breaks to **10** and the **labels** to *dollar format*;
8. label the x-axis **Gender** and the y-axis **Base Pay**;
9. use **theme_hc()**.

Display **mod_1_plot** by typing its name.

**Questions 5.4**: Answer these questions:
(1) Do *men* outearn *women* irrespective of *department*?
(2) Is there much of an *interaction effect* between *gender* and *department*? (Hint: you can also examine the *89% credible intervals* for the interaction regression coefficients to answer this question.)

**Responses 5.4**: *(1) Yes (2) Yes *.

```{r, task5_4}
mod_1_post_fit <- crossing(
  gender = levels(org_work$gender),
  dept = levels(org_work$gender)
  ) %>%
  add_fitted_draws(mod_1)


mod_1_post_pred <- crossing(
  gender = levels(org_work$gender),
   age = levels(org_work$gender)
  ) %>%
  add_predicted_draws(mod_1)



mod_1_plot <- ggplot(
  # data
  org_work,
  # mapping
  aes(x = gender, y = base_pay)
  ) +
  ## jitter observed data points
  geom_jitter(height = 0.05, width = 0.05, alpha = 0.5) +
  ## add posterior predicted values
  geom_jitter(
    # adjust height, width
    height = 0.05, width = 0.05, 
    # data
    data = mod_1_post_pred,
    # mapping
    mapping = aes(x = gender, y = .prediction),
    # color, size, alpha 
    color = "lightgreen", size = 0.5, alpha = 0.15
  ) +
  ## add posterior fitted values
  geom_jitter(
    # adjust height, width
    height = 0.05, width = 0.05, 
    # data
    data = mod_1_post_fit,
    # mapping
    mapping = aes(x = gender, y = .value),
    # color, size, alpha 
    color = "skyblue", size = 1.5, alpha = 0.15
  ) +
  ## add median posterior fitted values
  geom_point(
    # map fitted values
    aes(y = mod_1_fitted),
    # color, size
    color = "red", size = 2
  ) +
   facet_wrap(
    # facet by variable, 
    vars(dept), 
    # display across rows
    nrow = 2, 
    # labels
    labeller = as_labeller(
      # look-up table
      setNames(
        # vector elements
        paste("Department", 1:5, sep = ": "), 
        # names of elements
        1:5
      )
    ) 
  ) +
  ## scale y-axis
  scale_y_continuous(n.breaks = 10, labels = scales::dollar_format()) +
  ## labels
  labs(x = "Gender", y = "Base Pay") +
  #define theme
  theme_hc()

## display plot
mod_1_plot
```

## Task 6: Save Object

For this task, you will save a plot.

### Task 6.1

Save **mod_1_plot** as **bayes_reg.png** in the **plots** folder of the project directory using **ggsave()**.
Use a width of *9 inches* and height of *6 inches* for all plots.

```{r, task6_1}
#mod_1_plot
ggsave(
  here("plots", "bayes_reg.png"),
  plot = mod_1_plot,
  units = "in", width = 9, height = 6
)

```

## Task 7: Conceptual Question

For your last task, you will respond to a conceptual question.

**Question 7.1**: What is the difference between the *fitted* and *predicted* values produced by **add_fitted_draws()** and **add_predicted_draws()**, respectively?

**Response 7.1**: *Fitted values adds draws from posterior liner PREDICTORS to the data. Predicted values adds draws from posterior PREDICTIONS to the data. . *.
